R for Clinical Study Reports and Submission

### 2021-08-29 tlf-baseline.Rmd
update baseline table

# Table for Baseline Characteristics

@@

```{r}
library(table1)
library(r2rtf)
library(haven)
library(stringr)
```

@@

```{r}
tbl <- table1(~ SEX + AGE + RACE | TRT01P, data = adsl)
tbl
```

@@

```{r}
tbl_base <- tbl %>% 
              as.data.frame() %>% 
              mutate( across(everything(), 
                      ~ str_replace_all(.x, intToUtf8(160), " ") ) 
                    )

>>>>

# Baseline Characteristics

@@

```{r}
library(table1)
library(r2rtf)
library(haven)
library(dplyr)
library(tidyr)
library(stringr)
library(tools)
```

@@

```{r}
ana <- adsl %>% 
  mutate(SEX = factor(SEX, c("F", "M"), c("Female", "Male")), 
         RACE = toTitleCase(tolower(RACE)))

tbl <- table1(~ SEX + AGE + RACE | TRT01P, data = ana)
tbl
```

@@

```{r}
tbl_base <- tbl %>% 
              as.data.frame() %>% 
              as_tibble() %>%
              mutate( across(everything(), 
                      ~ str_replace_all(.x, intToUtf8(160), " ") ) 
                    )
